Doppler Imaging Fun

### 2019-06-13 tex/gitlinks.tex
rmeffect

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/d2fd278bdf8ebf22d2ce73093ca81d6bc0a4939b/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/32ee083fb652e476a27da13b2978124d3d330556/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
